Notes on Perturbational Quantities

### 2008-07-29 docs/pert_notes/paper.tex
removed a marginpar that we addressed in the code

We predict $\rho$ to edges using make\_edge\_scal in scalar\_advance.  The forcing term is set to zero, and therefor we set is\_conservative = T to alter the discretization in make\_edge\_scal.\MarginPar{I think there is a bug in the code since is\_conservative is always set to T, even if we are predicting $\rho'$.}

>>>>

We predict $\rho$ to edges using make\_edge\_scal in scalar\_advance.  The forcing term is set to zero, and therefor we set is\_conservative = T to alter the discretization in make\_edge\_scal.
